---
title: Ace Combat 7
author: ''
date: '2021-04-17'
slug: []
categories: []
tags: []
---

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(gridExtra)
library(patchwork)
c = read_csv("graph.csv")
```
Ace combat 7 is a flight simulation action game developed by Bandai Namco. The term `flight sim` is being very loosely used in this context as the controls are very arcade like and
planes will be carrying hundreds of missiles as well as rail guns or lasers.
However that is why most people find the game so enjoyable. It's always a great time to slap a rail gun onto a F-18 and take on 4 enemy squadrons single handedly.
My overall impression of the game is an 8/10, go play it.
However, I thought it would be interesting to take a more granular approach and look at what I think of certain missions. To help with this, I plotted out my overall enjoyment of all the missions in chronological order based on the story.

```{r,echo=FALSE,message=FALSE}
tab = c %>% group_by(Squadron) %>%
  summarise(Total_Missions = n(),Best_Score = max(Enjoyment),Worst_Score=min(Enjoyment),Average_Score=mean(Enjoyment))%>%tableGrob()

c = read_csv("graph.csv")
c$`Mission Name` = factor(c$`Mission Name`, levels = c$`Mission Name`)

pc = c %>% ggplot(aes(x = `Mission Name`,y=Enjoyment,color=Squadron,fill=Squadron))+
  geom_bar(stat="identity")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

pc/tab
```
This review will remain mostly spoiler free, but describing some of the general plot points will be important for this next part.
You play as a pilot that gets transferred to different squadrons as the story progresses.
I mention this specifically because a large part of the story is presented through mission briefings and radio chatter during missions. The characters giving these all change as you play your way through the game.
I wanted to see if my opinions on missions had any correlation with which squadron they take place with.

The squadron with the lowest score is Mage. This makes sense because they are very much the tutorial squad.
Most of these missions involve taking down bombers that barely fight back.
The wingmen and AWACS you get paired with are fairly unremarkable. However, this may be due to the fact that you're only with them for 4 missions.
Even the high point of this arc is really just about setting the player up for the next squadron they get sent to.

Spare squadron is the penal unit the player finds themselves on after leaving Mage.
The silliness of the plan to give a bunch of war criminals access to several multi-million dollar jets is only the first of many aspects I loved about my time with Spare squad.
The missions ramp up in difficulty and enjoyment. Most importantly is that all the characters you interact with at this time are memorable.
Mostly due to the conflict that exists between the squad and their jailers/commanding officers.
A perfect example of this is the first mission you play with them, 444.
During the mission briefing several pilots get sent to solitary confinement, on the runway one of your wingmen ignores air traffic control to force a takeoff and tells them to 'go to hell,' and when you finally get in the air you're told to just fly around with your weapons disabled to draw enemy fire.
In the span of less than a minute more characterization has been done for Spare than Mage.
The constant bickering and banter heard over the radio as you play these missions is part of why the missions with Spare have the highest average rating.

Unfortunately, all of that development goes down the drain when you leave Spare and are placed on Strider.
You're with them for the rest of the game and half of all the missions.
Despite this, I honestly couldn't tell you anything about the wingmen you're with for the remainder of the game.
The time spent with Strider scores well mostly because of the several boss battles and missions having some of the best [songs](https://www.youtube.com/watch?v=2o_XGQ3EcrI) in the game.

Story points aside, Ace Combat is an incredibly fun time and I would highly recommend it.



